### 2017-04-10 cthpc-2017/puyuma.tex
Create the paper prototype for puyuma.

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}

\usepackage{url}
\usepackage{listings}
% \usepackage{sectsty}
% \usepackage{authblk}
% \graphicspath{{../pdf/}{../jpeg/}}
% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}

\author{
\IEEEauthorblockN{
\bf
Sheng-Wen Cheng\IEEEauthorrefmark{1},
Shao-Hua Wang\IEEEauthorrefmark{2},
Po-Sheng Chen\IEEEauthorrefmark{2},
Keng-Fu Hsu\IEEEauthorrefmark{2},
Chun-Yi He\IEEEauthorrefmark{2},
Ching-Chun (Jim) Huang\IEEEauthorrefmark{3}}

\IEEEauthorblockA{
\IEEEauthorrefmark{1}Department of Computer Science and Information Engineering,\\Providence University, Taiwan}

\IEEEauthorblockA{
\IEEEauthorrefmark{2}Department of Engineering Science,\\National Cheng Kung University, Taiwan}

\IEEEauthorblockA{
\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering,\\National Cheng Kung University, Taiwan}
}

\begin{document}

\title{Title}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}
\section{Related Work}

\section{System Architecture}

This section introduces what was integrated into our autonomous vehicle system, and how this work leverage the whole system. The overall system architecture is shown in figure \ref{fig:overall_arch}.

\subsection{Robot Operating System(ROS)}

Robot Operating System, or ROS, is a system designed for robot. Instead a operating system, it’s a framework above operating system, proposing a identical interface around different machine architecture. As a middleware for interprocess communication, ROS takes a publish–subscribe pattern for data transfer abstraction. The implementation support multiple programming language API, enhance the system flexibility and scalability.

Moreover, ROS is a open-source collaborative platform. Developers around the world share their research across many field,like navigation, manipulation and perception. Based on this, other developers could save much cost for frastructure and concentrate on their own work.

\subsection{Hard Real-Time Operating System - Xenomai}

Real-time operating system (RTOS) guarantees the response time of real time task within specified time constraints, often referred to as “deadline”. A soft real-time OS can usually or generally meet a deadline, and a hard real-time OS can always meet a deadline deterministically. The real-time Linux extension for this project is Xenomai which provides two mechanisms, Cobalt and Mercury, to implement the real-time task. This paper just mention the Cobalt mechanism which we used for the autonomous vehicle system. Xenomai built the small extension named Cobalt into the Linux kernel,shown in figure \ref{fig:xeno_arch}, dealing with all time-critical activities, such as handling interrupts, and scheduling real-time threads. The Cobalt core has higher priority over the native Linux kernel. With the Cobalt mechanism, this project benefits from the RTOS API provided by Xenomai and abundant Linux services provided by native Linux kernel. As the above, this project also gains the portability since the real time environment based on Linux.

\begin{figure}
\centering
\includegraphics[width=3in]{img/arch.png}
\caption{System Architecture}
\label{fig:overall_arch}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3in]{img/xeno_arch.png}
\caption{Xenomai Cobalt Architecture}
\label{fig:xeno_arch}
\end{figure}

\subsection{Hardware}

For pursuing inexpensive and stable autonomous vehicle system, we limited the budgets within 4000 NTD, but the autonomous vehicle still has abilities of lane following, multiple car Interaction and route planning. The table \ref{hardware_list} shows the overall budgets.

\begin{table}
\centering
\caption{Hardware List}
\label{hardware_list}
\begin{tabular}{ll}
Hardware                & Budgets  \\
Raspberry Pi3 Model B   & 1600 NTD \\
Raspberry Pi camera     & 698 NTD  \\
2S LiPo battery 1300mAh & 240 NTD  \\
Sandisk 16G microSD     & 185 NTD  \\
L298N motor driver      & 263 NTD  \\
Car frame               & 375 NTD  \\
DC voltage regulator    & 105 NTD  \\
Total                   & 3466 NTD
\end{tabular}
\end{table}

\section{Implementation}
\subsection{Customized Linux Kernel}

The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase cache miss probability. In order to minimize the latency effect from Linux kernel, we remove the unnecessary kernel module and file system to reduce the kernel module size. In addition, we adjust the performance related kernel configuration to ease the burden of interrupt handling.

\subsection{KsoftPWM}

The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase cache miss probability. In order to minimize the latency effect from Linux kernel, we remove the unnecessary kernel module and file system to reduce the kernel module size. In addition, we adjust the performance related kernel configuration to ease the burden of interrupt handling.

\subsection{Lane Following Algorithm}

\subsubsection{Calibration}

Camera calibration is a early stage mission before doing the computer vision. There are two set of parameters need to be found, intrinsic parameters and extrinsic parameter. By estimate them we can know the relation between 2D image plane and 3D world.

The intrinsic matrix describes the projection from 3D world into 2D image plane. The ideal linear model is consist of focal length, pixel size and principal point. The nonlinear effect like lens distortion are also important however can not described in the linear camera model and usually solved by numerical methods. Figure \ref{fig:intrinsic} shows the effect of intrinsic calibration; The extrinsic matrix describes the translation and rotation of camera with respect to the world frame, which means the angle and position of camera taking pictures in 3D world. Applying extrinsic matrix causes ground projection, showed in Figure \ref{fig:extrinsic}, which is like a bird eye view.

\begin{figure}
\centering
\includegraphics[width=3.5in]{img/intrinsic.png}
\caption{Camera Undistortion}
\label{fig:intrinsic}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=2in]{img/extrinsic.png}
\caption{Ground Projection}
\label{fig:extrinsic}
\end{figure}

\subsubsection{Segment Detection}

Before the pose estimation, first have to do is to detect the lane segments from the image. The lane detector can be achieved by using Canny edge detection, color thresholding method and Hough transform.

First, transform the image from RGB color space into the HSV color space then use the color thresholding method to find the interested color like yellow or white in the image. Next, use Canny edge detection to detect the edges in the image, and use the bitwise and operation on color thresholding image and Canny edge image. This is a preparation step for Hough transform. Finally, apply the Hough Line transform comes out the segments.

Although the lane detector can find the segments, we still need to know the side of the lane mark that the segments is on, which is much important to pose estimation. Segment side can be determined by reading multiple pixels in both positive and negative direction of the segment normal vector on color thresholded image. Figure \ref{fig:lane_detect} visualizes the segment locations and segment sides, and also shows the values of $d$ and $\phi$. The lane detector only works at the bottom ROI(Region of Interest) part because there is much possible to be the lane.

\begin{figure}
\centering
\includegraphics[width=2in]{img/lane_detect.png}
\caption{Segments visualization}
\label{fig:lane_detect}
\end{figure}

\subsubsection{Frame Transformation}

For ease of calculation, apply extrinsic matrix that transforms the image from car's view to the road upper view  to the segments, causing a straightforward coordinate parallel to lane.
Moreover, The camera on the car is mounted in a distance from the origin. In order to know the real lateral displacement of the car, a transformation is need for converting camera frame into car frame.

\subsubsection{Pose Estimation for Single Segment}

Due to the lane geometry, each of the segment that lane detector detects can be calculated to be a single pose data with respect to the lane, $d$ is the lateral displacement and $\phi$ is the orientation angle. We will put the data into the histogram filter for data filtering later. The process is similar to vote so we call it a vote generating function.

\subsubsection{Histogram Filter}

The segment poses generated in previous process will then be voted into the histogram filter. The histogram filter will find out the mode of these datas and eliminate the data out of the mode with certain range, i.e., the noise. After that, calculate the \textbf{mean} of the rest of the datas comes out a much accurate pose information.

\subsubsection{Controller}We build a differential wheeled car, on which there are two independent motors. The car can be turn by changing the speed rate between two motors, hence it does not require any additional steering mechanics.
	We use the well known algorithm \textbf{"PID controller"} to fix the orientation and lateral displacement.

The equation of PID controller in continuous time is given as:

\[e(t) = setpoint(t) - x(t)\]

\[u(t) = K_p e(t) + K_i \int_{0}^{t} e(\tau) d\tau + K_d  \frac{de(t)}{dt}\]

and for discrete time:

\[e[t] = setpoint[t] - x[t]\]

\[u[t] = K_p e[t] + K_i \sum_0^t e[t] \Delta t + K_d \frac{e[t] - e[t-1]}{\Delta t}\]

	The pose controller is a cascaded PID controller.The $\phi$ controller is a low level controller for lane orientation stabilizing, and d controller fix the lateral displacement by changing the setpoint of $\phi$ controller to turn left or right.
The wheel control signal (PWM) is simply the throttle value plus the correction value:

\begin{lstlisting}
pwm_left = THROTTLE__BASE - pwm_correction
pwm_right = THROTTLE__BASE + pwm_correction
\end{lstlisting}

\begin{figure}
\centering
\includegraphics[width=3.5in]{img/controller.png}
\caption{Control Diagram}
\label{fig:controller}
\end{figure}

\subsection{Multiple Car Interaction}

\subsubsection{Apriltag}

Apriltag is a visual fiducial system. It appears as 2D bar code and stores data like QRcode. The difference is that Apriltag contains less data but provides farther and clearer data fetching, regardless of the orientation of view. Thus, it is useful for a wide variety of tasks including augmented reality, robotics, and camera calibration. The AprilTag detection software computes the precise 3D position, orientation, and identity of the tags relative to the camera. The 36h11 Apriltag family is adopted in this project to simulate scenario, like intersections, bus stops, traffic signal and parking lot.

\subsubsection{Crossroad}

Instead of using traditional and inefficient traffic light, we implement central management toward city crossroads. Before crossing a intersection, cars send request to the server according to the apriltag nearby which determines the crossroad ID. We predefine several states when multiple car intend to pass through the crossroad. For some situation, cars can pass at the same time, and others cannot, whereas need to set a lock until one car leaves 	the crossroad.

\section{Performance}

Based on the works mentioned above, this section we present some experimental results that quantify the performance of the system real time ability on stressed environment. In addition, we measure three kinds of tasks which were executed in user space, kernel space and irq task, respectively. We also compare performance of KsoftPWM, non-real-time PWM kernel module (nRTPKM) and WiringPi, the most famous library for GPIO controlling on Raspberry Pi.

	The measurement were obtained using Raspberry Pi 3 with 1.2GHz ARM Cortex-A53 CPU on a Broadcom bcm2709 chip, and the system load was generated by Linux Test Project (LTP). Linux Test Project provides a collection of tools for validating the reliability, robustness, and stability of Linux. Unit of latency is microsecond in all measurement.

\subsection{System Real-Time Performance}

Real-time performance is measured by stressing the system with LTP and applying cyclictest. We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus. Figure \ref{fig:stock_kernel_perf} shows the latency distribution in stock kernel. In contrast, measurement in Xenomai environment, shown in figure \ref{fig:xeno_perf}, obviously, Xenomai provides much better real-time performance. The customized kernel present better real-time ability in the user and kernel space, shown in figure \ref{fig:xeno_perf_modify}. Table \ref{xeno_compare} records the maximum latency for Xenomai in both original and customized kernel.

\begin{figure}
\centering
\includegraphics[width=2in]{img/stock_kernel.png}
\caption{Stock Kernel Performance}
\label{fig:stock_kernel_perf}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=2in]{img/xenomai_load.png}
\caption{Xenomai Performance}
\label{fig:xeno_perf}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=2in]{img/xenomai_load_modify.png}
\caption{Customized Xenomai Performance}
\label{fig:xeno_perf_modify}
\end{figure}

\begin{table}[]
\centering
\caption{Maximum latency for Xenomai}
\label{xeno_compare}
\begin{tabular}{llll}
                              & User task & Kernel task & Irq task \\
Xenomai with original kernel  & 76.067 us & 36.262 us   & 27.895us \\
Xenomai with customized kernel & 42.678us  & 29.973us    & 27.11us 
\end{tabular}
\end{table}

\subsection{KsoftPWM}

The KsoftPWM performs better real-time ability than the others, shown in figure \ref{fig:ksoftpwm_perf}. The WiringPi real-time ability is similar to nRTPKM, since both of them are not in Xenomai environment and perform like the stock kernel. The difference of minimum latency between WiringPi and nRTPKM was caused by different implementation. nRTPKM uses sleep function to simulate the PWM signal, and WiringPi uses busy-waiting delay function to implement which may cause higher system load.

\begin{figure}
\centering
\includegraphics[width=2in]{img/ksoftpwm_load.png}
\caption{PWM Task Performance}
\label{fig:ksoftpwm_perf}
\end{figure}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}

### 2017-04-10 cthpc-2017/puyuma.tex
Correct the spelling and add the \FloatBarrier in Latex.

@@
 \usepackage[caption=false,font=footnotesize]{subfig}
+\usepackage{placeins}
+%\usepackage{flafter}
 
@@
 
+\FloatBarrier
+\begin{figure}
+	\centering
+	\includegraphics[width=3in]{img/arch.png}
+	\caption{System Architecture}
+	\label{fig:overall_arch}
+\end{figure}
+
 \subsection{Robot Operating System(ROS)}
@@
 Instead a operating system, it’s a framework above operating system, proposing a identical interface around different machine architecture.
-As a middleware for interprocess communication, ROS takes a publish–subscribe pattern for data transfer abstraction.
+As a middleware for interprocess communication, ROS takes a publish-subscribe pattern for data transfer abstraction.
 The implementation support multiple programming language API, enhance the system flexibility and scalability.
@@
 With the Cobalt mechanism, this project benefits from the RTOS API provided by Xenomai and abundant Linux services provided by native Linux kernel.
-As the above, this project also gains the portability since the real time environment based on Linux.
-
-\begin{figure}
-\centering
-\includegraphics[width=3in]{img/arch.png}
-\caption{System Architecture}
-\label{fig:overall_arch}
-\end{figure}
+As the above, this project also gains the portability since the real time environment is based on Linux.
 
@@
 \end{figure}
+\FloatBarrier
 
@@
 \end{table}
+\FloatBarrier
 
@@
 
-The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase cache miss probability.
+The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase probability of cache miss.
 In order to minimize the latency effect from Linux kernel, we remove the unnecessary kernel module and file system to reduce the kernel module size.
@@
 
-The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase cache miss probability.
-In order to minimize the latency effect from Linux kernel, we remove the unnecessary kernel module and file system to reduce the kernel module size.
-In addition, we adjust the performance related kernel configuration to ease the burden of interrupt handling.
+Most system use pulse width modulation (PWM) to simulate the analog signal for smooth motor controlling.
+PWM signal was often generated by hardware, known as hardware PWM.
+On the contrary, using general-purpose input/output (GPIO) to simulate the PWM signal, known as software PWM.
+
+We built the software PWM kernel module with Xenomai real-time API, we named it KsoftPWM, for this project.
+With the real-time application, it ensures the precision of KsoftPWM signal generation.
+Furthermore, the KsoftPWM was built in kernel space to eliminate the system call overhead from user space.
 
@@
 
-Camera calibration is a early stage mission before doing the computer vision.
+Camera calibration is an early stage mission before doing the computer vision.
 There are two set of parameters need to be found, intrinsic parameters and extrinsic parameter.
@@
 
+\FloatBarrier
 \begin{figure}
@@
 
+\FloatBarrier
 \begin{figure}	
@@
 
-\subsection{System Real-Time Performance}
-
-Real-time performance is measured by stressing the system with LTP and applying cyclictest.
-We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus.
-Figure \ref{fig:stock_kernel_perf} shows the latency distribution in stock kernel.
-In contrast, measurement in Xenomai environment, shown in figure \ref{fig:xeno_perf}, obviously, Xenomai provides much better real-time performance.
-The customized kernel present better real-time ability in the user and kernel space, shown in figure \ref{fig:xeno_perf_modify}.
-Table \ref{xeno_compare} records the maximum latency for Xenomai in both original and customized kernel.
-
+\FloatBarrier
 \begin{figure}	
@@
 
+\subsection{System Real-Time Performance}
+
+Real-time performance is measured by stressing the system with LTP and applying cyclictest.
+We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus.
+Figure \ref{fig:stock_kernel_perf} shows the latency distribution in stock kernel.
+In contrast, measurement in Xenomai environment, shown in figure \ref{fig:xeno_perf}, obviously, Xenomai provides much better real-time performance.
+The customized kernel present better real-time ability in the user and kernel space, shown in figure \ref{fig:xeno_perf_modify}.
+Table \ref{xeno_compare} records the maximum latency for Xenomai in both original and customized kernel.
+
 \subsection{KsoftPWM}
@@
 nRTPKM uses sleep function to simulate the PWM signal, and WiringPi uses busy-waiting delay function to implement which may cause higher system load.
+
+\FloatBarrier
 

### 2017-04-20 cthpc-2017/puyuma.tex
add abstract

@@
 
-\title{Title}
+\title{Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles}
 
@@
 \begin{abstract}
+A holistic design and cost-efficient platform to construct self-driving systems is presented, with an emphasis on Linux-based software architectures for computer vision, control system, and inter-vehicle communication.
+Starting with an executable specification of autonomous car application, subsequent transformations are performed across different levels of abstraction until the final implementation is achieved.
+The software partitioning is facilitated through the integration of ROS and OpenCV in the same design environment, as well as closed-loop control algorithms and Linux in the run-time system.
+We built a rapid prototyping based on fundamentally open source technologies, bill of material (BOM) under 100 dollars USD, which allows developers to be explored and evaluated in realistic conditions efficiently.
+Using lane departure and the corresponding performance speedup, we show that our platform reduces the design time, while improving the verification efforts, with the aid of tweaked real-time executives.
 \end{abstract}

### 2017-04-20 cthpc-2017/paper.tex
Use consistent naming

--- 2017-04-20 cthpc-2017/puyuma.tex
@@
 The software partitioning is facilitated through the integration of ROS and OpenCV in the same design environment, as well as closed-loop control algorithms and Linux in the run-time system.
-We built a rapid prototyping based on fundamentally open source technologies, bill of material (BOM) under 100 dollars USD, which allows developers to be explored and evaluated in realistic conditions efficiently.
+We built a rapid prototyping based on fundamentally open source technologies and hardware under 100 dollars USD, which allows developers to be explored and evaluated in realistic conditions efficiently.
 Using lane departure and the corresponding performance speedup, we show that our platform reduces the design time, while improving the verification efforts, with the aid of tweaked real-time executives.
@@
 \section{Introduction}
+As an example of Autonomous vehicles, the Google Car has already succeeded in covering thousands of miles of real-road driving \cite{autonomous}.
+
 \section{Related Work}
@@
 
-Moreover, ROS is a open-source collaborative platform.
+Moreover, ROS is an open-source collaborative platform.
 Developers around the world share their research across many field,like navigation, manipulation and perception.
@@
 
-\subsection{KsoftPWM}
+\subsection{Software-based PWM}
 
@@
 
-We built the software PWM kernel module with Xenomai real-time API, we named it KsoftPWM, for this project.
+We built the software PWM kernel module with Xenomai real-time API, named after KsoftPWM.
 With the real-time application, it ensures the precision of KsoftPWM signal generation.

### 2017-04-20 cthpc-2017/paper.tex
Revise price info

@@
 		Hardware                & Budgets  \\
-		Raspberry Pi3 Model B   & 1600 NTD \\
+		Raspberry Pi3 Model B   & 1200 NTD \\
 		Raspberry Pi camera     & 698 NTD  \\
@@
 		DC voltage regulator    & 105 NTD  \\
-		Total                   & 3466 NTD
+		Total                   & 3066 NTD
 	\end{tabular}

### 2017-04-20 cthpc-2017/paper.tex
preliminary introduction

@@
 \section{Introduction}
-As an example of Autonomous vehicles, the Google Car has already succeeded in covering thousands of miles of real-road driving \cite{autonomous}.
+As an example of autonomous vehicles, the Google Car has already succeeded in covering thousands of miles of real-road driving \cite{autonomous} with the promising benefits by increasing traffic efficiency \cite{traffic-flow}, reducing pollution \cite{reduce-pollution}, and eliminating up to 90\% of traffic accidents \cite{traffic-accident}.
+However, it is not straightforward for most people to build an autonomous vehicle due to very high bill of materials (BOM) and sufficient system software infrastructure, that prevents from potential innovations and collobrations, especially to arising maker movement \cite{maker}.
 

### 2017-04-20 cthpc-2017/paper.tex
rearrange figures
Reorganize

@@
 \IEEEauthorblockA{
-\IEEEauthorrefmark{1}Department of Computer Science and Information Engineering,\\Providence University, Taiwan}
+\IEEEauthorrefmark{1}Department of Computer Science and Information Engineering, Providence University, Taiwan}
 
 \IEEEauthorblockA{
-\IEEEauthorrefmark{2}Department of Engineering Science,\\National Cheng Kung University, Taiwan}
+\IEEEauthorrefmark{2}Department of Engineering Science, National Cheng Kung University, Taiwan}
 
 \IEEEauthorblockA{
-\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering,\\National Cheng Kung University, Taiwan}
+\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Cheng Kung University, Taiwan}
 }
@@
 
+The goal of this research was to adapt open source foundation and to design algorithms for a self-driving miniature vehicle, which should be able to reliably follow lane markings, overtake stationary obstacles, and park automatically for inexpensive hardware configurations.
+We explicitly explore the possibility to not only exploit hardware components but also the software/hardware interface to read data from sensors and to control the actors for steering and acceleration, which was evaluated by various system services of the incorporation of the real-time extension for GNU/Linux.
+Afterwards, a short overview of the development process and the evaluation of the software is presented.
+
 \section{Related Work}
+
+In this section, we concentrate on currently available frameworks for the development of component-based embedded automotive and robotics software.
+
+In 2016, MIT CSAIL took students on a trip to "Duckietown" \cite{Duckietown} to create self-driving taxis that can navigate the roads of a model city with just a single on-board camera and no pre-programmed maps.
+Students developed algorithms to read traffic signs and notice pedestrian-ducks, and learned to integrate different disciplines like control theory, machine learning, and computer vision into their systems.
+Eventually, MIT distributes all the lecture materials, middleware, drivers, ROS modules, and etc.
+as open source software.
+
+AUTOSAR (AUTomotive Open System ARchitecture) is a standardized architecture for automotive software systems.
+Its primary focus is the system development process for electronic control units (ECU) and does not provide specific support for sensor/actuator-based autonomou ssystem development \cite{rtes}.
+An implementation of an AUTOSAR-compliant embedded software platform is Arctic Core \cite{arctic-core}, offering a real-time operating system, memory services, and communication services such as CAN and LIN.
+
+In recent years, the Robot Operating System (ROS) \cite{ROS} incorporates the simulationenvironment Player/Stage/Gazebo \cite{player/stage}, and it has been widely adopted as a meta-OS for many popular robotic platforms.
+The abstraction of physical sensors and actuators enables ROS to support a wide range of robotics platform and reuse of components by implementing publish-subscribe design pattern for inter-component communications.
 
@@
 
-This section introduces what was integrated into our autonomous vehicle system, and how this work leverage the whole system. The overall system architecture is shown in figure \ref{fig:overall_arch}.
+The overall system architecture is shown in figure \ref{fig:overall_arch}.
 
-\FloatBarrier
 \begin{figure}
@@
 
-\subsection{Robot Operating System(ROS)}
-
-Robot Operating System, or ROS, is a system designed for robot.
-Instead a operating system, it’s a framework above operating system, proposing a identical interface around different machine architecture.
-As a middleware for interprocess communication, ROS takes a publish-subscribe pattern for data transfer abstraction.
-The implementation support multiple programming language API, enhance the system flexibility and scalability.
-
-Moreover, ROS is an open-source collaborative platform.
-Developers around the world share their research across many field,like navigation, manipulation and perception.
-Based on this, other developers could save much cost for frastructure and concentrate on their own work.
-
-\subsection{Hard Real-Time Operating System - Xenomai}
-
-Real-time operating system (RTOS) guarantees the response time of real time task within specified time constraints, often referred to as “deadline”.
-A soft real-time OS can usually or generally meet a deadline, and a hard real-time OS can always meet a deadline deterministically.
-The real-time Linux extension for this project is Xenomai which provides two mechanisms, Cobalt and Mercury, to implement the real-time task.
-This paper just mention the Cobalt mechanism which we used for the autonomous vehicle system.
-Xenomai built the small extension named Cobalt into the Linux kernel,shown in figure \ref{fig:xeno_arch}, dealing with all time-critical activities, such as handling interrupts, and scheduling real-time threads.
-The Cobalt core has higher priority over the native Linux kernel.
-With the Cobalt mechanism, this project benefits from the RTOS API provided by Xenomai and abundant Linux services provided by native Linux kernel.
-As the above, this project also gains the portability since the real time environment is based on Linux.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=3in]{img/xeno_arch.png}
-	\caption{Xenomai Cobalt Architecture}
-	\label{fig:xeno_arch}
-\end{figure}
-\FloatBarrier
-
 \subsection{Hardware}
 
-For pursuing inexpensive and stable autonomous vehicle system, we limited the budgets within 4000 NTD, but the autonomous vehicle still has abilities of lane following, multiple car Interaction and route planning.
+For pursuing inexpensive and stable autonomous vehicle system, we limited the budget under 100 dollars USD, but the autonomous vehicle still has abilities of lane following, multiple car Interaction and route planning.
 The table \ref{hardware_list} shows the overall budgets.
@@
 	\centering
-	\caption{Hardware List}
+	\caption{Bill Of Materials}
 	\label{hardware_list}
@@
 \end{table}
-\FloatBarrier
 
 \section{Implementation}
-\subsection{Customized Linux Kernel}
 
-The Linux kernel is resident in memory after the booting stage, therefore the large kernel image and kernel module size may increase probability of cache miss.
-In order to minimize the latency effect from Linux kernel, we remove the unnecessary kernel module and file system to reduce the kernel module size.
-In addition, we adjust the performance related kernel configuration to ease the burden of interrupt handling.
+\subsection{Hard Real-Time Operating System}
 
-\subsection{Software-based PWM}
+RTOS guarantees the response time of real time task within specified time constraints \cite{RTOS}, often referred to as "deadline", and a hard real-time OS can always meet a deadline deterministically.
+We adopt Xenomai \cite{Xenomai}, an open source real-time Linux extension, allowing periodic preemptive hard real-time tasks along with typical Linux kernel and userspace.
+The Cobalt core in Xenomai 3 is a co-kernel which supplements the Linux kernel for delivering real-time services with very low latency \cite{rtlws2015}, shown i0n figure \ref{fig:xeno_arch}, dealing with all time-critical events, such as interrupt handling, and scheduling real-time threads.
+Cobalt core, thereby has higher priority over Linux kernel.
+Our self-driving car benefits from deterministic behavior in Xenomai 3.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=3in]{img/xeno_arch.png}
+	\caption{Cobalt core in Xenomai 3}
+	\label{fig:xeno_arch}
+\end{figure}
 
@@
 
-Camera calibration is an early stage mission before doing the computer vision.
-There are two set of parameters need to be found, intrinsic parameters and extrinsic parameter.
-By estimate them we can know the relation between 2D image plane and 3D world.
+Camera calibration is an early stage mission before performing computer vision operations.
+There are two sets of parameters needed to be found: intrinsic parameters and extrinsic parameter.
+By estimating them we can know the relation between 2D image plane and 3D world.
 
@@
 \end{figure}
-\FloatBarrier
 
@@
 
-\FloatBarrier
 \begin{figure}
@@
 
-\FloatBarrier
 \begin{figure}	
@@
 
-\FloatBarrier
-
 \begin{figure}

### 2017-04-20 cthpc-2017/paper.tex
Syntax tweaks

@@
 
-For pursuing inexpensive and stable autonomous vehicle system, we limited the budget under 100 dollars USD, but the autonomous vehicle still has abilities of lane following, multiple car Interaction and route planning.
-The table \ref{hardware_list} shows the overall budgets.
+We limited the budget of whole hardware under 100 dollars USD, but the autonomous vehicle prototype still has abilities of lane following, multiple car Interaction and route planning.
+The table \ref{hardware_list} shows the details.
 
@@
 We adopt Xenomai \cite{Xenomai}, an open source real-time Linux extension, allowing periodic preemptive hard real-time tasks along with typical Linux kernel and userspace.
-The Cobalt core in Xenomai 3 is a co-kernel which supplements the Linux kernel for delivering real-time services with very low latency \cite{rtlws2015}, shown i0n figure \ref{fig:xeno_arch}, dealing with all time-critical events, such as interrupt handling, and scheduling real-time threads.
+The Cobalt core in Xenomai 3 is a co-kernel which supplements the Linux kernel for delivering real-time services with very low latency \cite{rtlws2015}, shown in figure \ref{fig:xeno_arch}, dealing with all time-critical events, such as interrupt handling, and scheduling real-time threads.
 Cobalt core, thereby has higher priority over Linux kernel.
@@
 The intrinsic matrix describes the projection from 3D world into 2D image plane.
-The ideal linear model is consist of focal length, pixel size and principal point.
-The nonlinear effect like lens distortion are also important however can not described in the linear camera model and usually solved by numerical methods.
+The ideal linear model consists of focal length, pixel size and principal point.
+The nonlinear effect like lens distortion are also important, but it can not be described in the linear camera model, usually solved by numerical methods.
 Figure \ref{fig:intrinsic} shows the effect of intrinsic calibration; The extrinsic matrix describes the translation and rotation of camera with respect to the world frame, which means the angle and position of camera taking pictures in 3D world.
@@
 
-Before the pose estimation, first have to do is to detect the lane segments from the image.
-The lane detector can be achieved by using Canny edge detection, color thresholding method and Hough transform.
-
-First, transform the image from RGB color space into the HSV color space then use the color thresholding method to find the interested color like yellow or white in the image.
-Next, use Canny edge detection to detect the edges in the image, and use the bitwise and operation on color thresholding image and Canny edge image.
+Before pose estimation, we have to detect lane segments from the retrieved images in advance.
+It can be achieved by using Canny edge detection, color thresholding method and Hough transform.
+First, we transform the image from RGB color space into the HSV color space then use the color thresholding method to find the interested color like yellow or white in the image.
+Next, we apply Canny edge detection to detect the edges in the image, and use the bitwise and operation on color thresholding image and Canny edge image.
 This is a preparation step for Hough transform.
@@
 
-Although the lane detector can find the segments, we still need to know the side of the lane mark that the segments is on, which is much important to pose estimation.
+Although the lane detector can find the segments, we still need to be aware of the side of lane mark that the segments is on, which is much important to pose estimation.
 Segment side can be determined by reading multiple pixels in both positive and negative direction of the segment normal vector on color thresholded image.

### 2017-04-20 cthpc-2017/paper.tex
Add conclusion

@@
 Most system use pulse width modulation (PWM) to simulate the analog signal for smooth motor controlling.
-PWM signal was often generated by hardware, known as hardware PWM.
-On the contrary, using general-purpose input/output (GPIO) to simulate the PWM signal, known as software PWM.
-
-We built the software PWM kernel module with Xenomai real-time API, named after KsoftPWM.
-With the real-time application, it ensures the precision of KsoftPWM signal generation.
-Furthermore, the KsoftPWM was built in kernel space to eliminate the system call overhead from user space.
+PWM signals are often generated by certain hardware.
+On the contrary, using general-purpose input/output (GPIO) to simulate PWM signals is known as software PWM.
+We implement the later as a Xenomai kernel-mode real-time task to ensure the precision of PWM signal generation, named after KsoftPWM, for closed-loop control system, benefiting from the limination of system call overhead and potential locks.
 
@@
 
-For ease of calculation, apply extrinsic matrix that transforms the image from car's view to the road upper view  to the segments, causing a straightforward coordinate parallel to lane.
-Moreover, The camera on the car is mounted in a distance from the origin.
-In order to know the real lateral displacement of the car, a transformation is need for converting camera frame into car frame.
+To reduce computation efforts, we apply extrinsic matrix that transforms the image from car's view to the road upper view to the segments, causing a straightforward coordinate parallel to lane.
+Moreover, the car camera is mounted in a distance from the origin.
+In order to know the real lateral displacement of the car, a transformation is needed for converting camera frame into car frame.
 
@@
 
-	The pose controller is a cascaded PID controller.The $\phi$ controller is a low level controller for lane orientation stabilizing, and d controller fix the lateral displacement by changing the setpoint of $\phi$ controller to turn left or right.
-The wheel control signal (PWM) is simply the throttle value plus the correction value:
+The pose controller is a cascaded PID controller.
+The $\phi$ controller is a low level controller for lane orientation stabilizing, and d controller fix the lateral displacement by changing the setpoint of $\phi$ controller to turn left or right.
+The wheel control signal generating PWM is simply the throttle value plus the correction value:
 
@@
 
-Based on the works mentioned above, this section we present some experimental results that quantify the performance of the system real time ability on stressed environment.
-In addition, we measure three kinds of tasks which were executed in user space, kernel space and irq task, respectively.
-We also compare performance of KsoftPWM, non-real-time PWM kernel module (nRTPKM) and WiringPi, the most famous library for GPIO controlling on Raspberry Pi.
-
-	The measurement were obtained using Raspberry Pi 3 with 1.2GHz ARM Cortex-A53 CPU on a Broadcom bcm2709 chip, and the system load was generated by Linux Test Project (LTP).
-Linux Test Project provides a collection of tools for validating the reliability, robustness, and stability of Linux.
+We executed tasks in user space, kernel space and irq task respectively, to evaluate real-time capability.
+We also compare performance among KsoftPWM, non-real-time PWM kernel module (nRTPKM) and WiringPi \cite{WiringPi}, the most famous library for GPIO controlling on Raspberry Pi 3 (Broadcom bcm2709 SoC, 1.2GHz ARM Cortex-A53 CPU).
+The background system load was generated by Linux Test Project (LTP), which provides a collection of tools for validating the reliability, robustness, and stability of Linux.
 Unit of latency is microsecond in all measurement.
-
-\begin{figure}	
-	\centering
-	\includegraphics[width=2in]{img/stock_kernel.png}
-	\caption{Stock Kernel Performance}
-	\label{fig:stock_kernel_perf}
-\end{figure}
 
@@
 We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus.
-Figure \ref{fig:stock_kernel_perf} shows the latency distribution in stock kernel.
-In contrast, measurement in Xenomai environment, shown in figure \ref{fig:xeno_perf}, obviously, Xenomai provides much better real-time performance.
-The customized kernel present better real-time ability in the user and kernel space, shown in figure \ref{fig:xeno_perf_modify}.
-Table \ref{xeno_compare} records the maximum latency for Xenomai in both original and customized kernel.
+Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in figure \ref{fig:xeno_perf_modify}.
+Table \ref{xeno_compare} records the maximum latency for Xenomai.
 
@@
 
-The KsoftPWM performs better real-time ability than the others, shown in figure \ref{fig:ksoftpwm_perf}.
-The WiringPi real-time ability is similar to nRTPKM, since both of them are not in Xenomai environment and perform like the stock kernel.
+The KsoftPWM outperforms in better real-time ability, shown in figure \ref{fig:ksoftpwm_perf}.
+The latency distribution of WiringPi is similar to nRTPKM, since both of them are just normal Linux userspace tasks rather than hard real-time one.
 The difference of minimum latency between WiringPi and nRTPKM was caused by different implementation.
-nRTPKM uses sleep function to simulate the PWM signal, and WiringPi uses busy-waiting delay function to implement which may cause higher system load.
+nRTPKM uses sleep function to simulate the PWM signals while WiringPi uses busy-waiting delay which may cause higher system load.
 
@@
 
+\section{Conclusion}
+
+This paper presents the hardware and software architecture of a self-driving miniature vehicle based entirely on cost-efficient components, that implies strategic values for the long term evaluation.
+RTOS should be very efficient in terms of resource usage and runtime.
+The context switching performance is important because the number of sensors can be high and we need to read data from different sensors continuously in real-time.
+Linux with real-time extension  fulfills all these criteria e.g., performance, reusability, changeability, and maintainability, whichhave significant value from the software engineer's perspective.
+Puyuma is released as an open source project as well as ROS, allowing further collaboration on algorithms and system integration.
+
 \bibliographystyle{IEEEtran}

### 2017-04-20 cthpc-2017/paper.tex
Revise wording

@@
 
-The overall system architecture is shown in figure \ref{fig:overall_arch}.
+The system is designed for multiple self-driving cars, enabling collaborative computer vision, map navigation, motor control, and wireless communications, shown in figure \ref{fig:overall_arch}.
+It aggregates local pose graphs obtained from its multiple cars into a global pose graph, which it then feeds back to the cars to increase their mapping and localization effectiveness.
 
@@
 
-We limited the budget of whole hardware under 100 dollars USD, but the autonomous vehicle prototype still has abilities of lane following, multiple car Interaction and route planning.
-The table \ref{hardware_list} shows the details.
+Despite limited the budget shown in table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car Interaction and route planning.
 

### 2017-04-20 cthpc-2017/paper.tex
Make it more consistent

@@
 
-The system is designed for multiple self-driving cars, enabling collaborative computer vision, map navigation, motor control, and wireless communications, shown in figure \ref{fig:overall_arch}.
+The system is designed for multiple self-driving cars, enabling collaborative computer vision, map navigation, motor control, and wireless communications, shown in Figure \ref{fig:overall_arch}.
 It aggregates local pose graphs obtained from its multiple cars into a global pose graph, which it then feeds back to the cars to increase their mapping and localization effectiveness.
@@
 We adopt Xenomai \cite{Xenomai}, an open source real-time Linux extension, allowing periodic preemptive hard real-time tasks along with typical Linux kernel and userspace.
-The Cobalt core in Xenomai 3 is a co-kernel which supplements the Linux kernel for delivering real-time services with very low latency \cite{rtlws2015}, shown in figure \ref{fig:xeno_arch}, dealing with all time-critical events, such as interrupt handling, and scheduling real-time threads.
+The Cobalt core in Xenomai 3 is a co-kernel which supplements the Linux kernel for delivering real-time services with very low latency \cite{rtlws2015}, shown in Figure \ref{fig:xeno_arch}, dealing with all time-critical events, such as interrupt handling, and scheduling real-time threads.
 Cobalt core, thereby has higher priority over Linux kernel.
@@
 We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus.
-Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in figure \ref{fig:xeno_perf_modify}.
+Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in Figure \ref{fig:xeno_perf_modify}.
 Table \ref{xeno_compare} records the maximum latency for Xenomai.
@@
 
-The KsoftPWM outperforms in better real-time ability, shown in figure \ref{fig:ksoftpwm_perf}.
+The KsoftPWM outperforms in better real-time ability, shown in Figure \ref{fig:ksoftpwm_perf}.
 The latency distribution of WiringPi is similar to nRTPKM, since both of them are just normal Linux userspace tasks rather than hard real-time one.

### 2017-04-20 cthpc-2017/paper.tex
Fix typo

@@
 As an example of autonomous vehicles, the Google Car has already succeeded in covering thousands of miles of real-road driving \cite{autonomous} with the promising benefits by increasing traffic efficiency \cite{traffic-flow}, reducing pollution \cite{reduce-pollution}, and eliminating up to 90\% of traffic accidents \cite{traffic-accident}.
-However, it is not straightforward for most people to build an autonomous vehicle due to very high bill of materials (BOM) and sufficient system software infrastructure, that prevents from potential innovations and collobrations, especially to arising maker movement \cite{maker}.
+However, it is not straightforward for most people to build autonomous vehicles due to very high bill of materials (BOM) and insufficient system software infrastructure, that prevents from potential innovations and collobrations, especially to arising maker movement \cite{maker}.
 

### 2017-04-24 cthpc-2017/paper.tex
Fix typo
Write acknowledgement

@@
 Real-time performance is measured by stressing the system with LTP and applying cyclictest.
-We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus.
+We use LTP $-i$ and $-c$ flags to specify the background CPU load with multiple processes and accessing on IO bus.
 Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in Figure \ref{fig:xeno_perf_modify}.
@@
 
+\section{Acknowledge}
+
+I begin my research in computer vision since I audited Prof. Nick Wang's lecture in National Chao Tung University in 2016, which is very inspiring.
+
+After the class, our advisor Jim Huang, leads us doing the real-time robotic research, and make us gain a lot of new knowledges in computer vision, operating system, communiucation system, control theory, etc.
+
+I want to thanks these professors, and my partners in National Cheng Kung University, especially Shao-Hua and Po-Sheng, without them, I would never able to achieve several key features of Puyuma.
+
+I also want to thanks Providence University for providing me fundations and space doing experiments, and my parent, who let me receive education without any worries.
+
 \bibliographystyle{IEEEtran}

### 2017-04-26 cthpc-2017/paper.tex
Rewrite ackknowldgement

--- 2017-04-20 cthpc-2017/paper.tex
@@
 
+\section{Acknowledge}
+
+We want to thanks Prof. Nick Wang from National Chao Tung University bringing Duckietown to Taiwan. His lecture and research inspired us very much.
+
 \bibliographystyle{IEEEtran}

### 2017-05-04 cthpc-2017/paper.tex
Improve Acknowledgements
Rewrite camera calibration section

@@
 
-Camera calibration is an early stage mission before performing computer vision operations.
-There are two sets of parameters needed to be found: intrinsic parameters and extrinsic parameter.
-By estimating them we can know the relation between 2D image plane and 3D world.
+The camera was calibrated before activating the controller. Two parameters are used to describe the relationship between image and real world: intrinsic matrix and extrinsic matrix.
 
-The intrinsic matrix describes the projection from 3D world into 2D image plane.
-The ideal linear model consists of focal length, pixel size and principal point.
-The nonlinear effect like lens distortion are also important, but it can not be described in the linear camera model, usually solved by numerical methods.
-Figure \ref{fig:intrinsic} shows the effect of intrinsic calibration; The extrinsic matrix describes the translation and rotation of camera with respect to the world frame, which means the angle and position of camera taking pictures in 3D world.
-Applying extrinsic matrix causes ground projection, showed in Figure \ref{fig:extrinsic}, which is like a bird eye view.
+The intrinsic matrix is also refer to the camera projection, it is an ideal linear model consists of focal length, pixel size and principal point, the non-linear effects like lens distortion[\ref{fig:intrinsic}] are usually solved numerically.
+
+The extrinsic matrix represents the rotation and translation of camera with respect to the world.
+A linear transformation called Homograpy is applied on  the matrix to change the camera view purely mathematically.
+
+Figure \ref{fig:extrinsic} show the result of Homography transformation, we exploit the transformation for the lane detectoion algorithm, the result is usually called the bird view image or inverse perspective mapping.
 
@@
 This is a preparation step for Hough transform.
-Finally, apply the Hough Line transform comes out the segments.
+Finally, apply gthe Hough Line transform comes out the segments.
 
@@
 
-We want to thanks Prof. Nick Wang from National Chao Tung University bringing Duckietown to Taiwan. His lecture and research inspired us very much.
+We would like to express our deep gratitude to Professor Nick Wang of National Chao Tung University in Taiwan for his enthusiastic encouragement on Duckietown lecture.
 

### 2017-05-04 cthpc-2017/paper.tex
Improve the description of lane following algorithm

@@
 	\includegraphics[width=3.5in]{img/intrinsic.png}
-	\caption{Camera Undistortion}
+	\caption{Camera undistortion}
 	\label{fig:intrinsic}
@@
 	\includegraphics[width=2in]{img/extrinsic.png}
-	\caption{Ground Projection}
+	\caption{Homography transformation (ground projection)}
 	\label{fig:extrinsic}
@@
 
-Before pose estimation, we have to detect lane segments from the retrieved images in advance.
-It can be achieved by using Canny edge detection, color thresholding method and Hough transform.
-First, we transform the image from RGB color space into the HSV color space then use the color thresholding method to find the interested color like yellow or white in the image.
-Next, we apply Canny edge detection to detect the edges in the image, and use the bitwise and operation on color thresholding image and Canny edge image.
-This is a preparation step for Hough transform.
-Finally, apply gthe Hough Line transform comes out the segments.
+The lane segment detection is performed before pose estimation.
+The ROI(Region of interest) is used to increase the accuracy by eliminate the region.
+Canny edge detection, HSV color thresholding and Hough transform are used to find the lane segments.
 
-Although the lane detector can find the segments, we still need to be aware of the side of lane mark that the segments is on, which is much important to pose estimation.
-Segment side can be determined by reading multiple pixels in both positive and negative direction of the segment normal vector on color thresholded image.
-Figure \ref{fig:lane_detect} visualizes the segment locations and segment sides, and also shows the values of $d$ and $\phi$.
-The lane detector only works at the bottom ROI(Region of Interest) part because there is much possible to be the lane.
+Figure \ref{fig:lane_detect} visualizes the lane pose and segments on the ROI region.
 
@@
 
-\subsubsection{Frame Transformation}
+\subsubsection{Pose Estimation}
 
-To reduce computation efforts, we apply extrinsic matrix that transforms the image from car's view to the road upper view to the segments, causing a straightforward coordinate parallel to lane.
-Moreover, the car camera is mounted in a distance from the origin.
-In order to know the real lateral displacement of the car, a transformation is needed for converting camera frame into car frame.
-
-\subsubsection{Pose Estimation for Single Segment}
-
-Due to the lane geometry, each of the segment that lane detector detects can be calculated to be a single pose data with respect to the lane, $d$ is the lateral displacement and $\phi$ is the orientation angle.
-We will put the data into the histogram filter for data filtering later.
-The process is similar to vote so we call it a vote generating function.
+We can generate the lane pose for every segments according to the lane geometry.
+The lane pose $d$ and $phi$ represent the car lateral displacement and orientation angle.
+we later feed this different poses into the histogram filter for a better prediction of the lane pose.
 
@@
 
-The segment poses generated in previous process will then be voted into the histogram filter.
-The histogram filter will find out the mode of these datas and eliminate the data out of the mode with certain range, i.e., the noise.
-After that, calculate the \textbf{mean} of the rest of the datas comes out a much accurate pose information.
+The histogram filter works like a vote box.
+We first filter out extreme value vote by the \textbf{mode}.
+We then calculate the \textbf{mean} of the rest of the data.
+Higher vote pose will have higher chance to dominate the result.
 
-\subsubsection{Controller}We build a differential wheeled car, on which there are two independent motors.
-The car can be turn by changing the speed rate between two motors, hence it does not require any additional steering mechanics.
-We use the well known algorithm \textbf{"PID controller"} to fix the orientation and lateral displacement.
+\subsubsection{Controller}
+
+We use the differential wheeled type car, which there are two independent motors on two side.
+The car can turn by changing the speed rate between two motors, therefore it doesn't requires a steering mechanics.
+We use the \textbf{PID Control} algorithm to fix the orientation and lateral displacement.
 

### 2017-05-05 cthpc-2017/paper.tex
Improve controller description

@@
 The lane segment detection is performed before pose estimation.
-The ROI(Region of interest) is used to increase the accuracy by eliminate the region.
+The ROI(Region of interest) is used to increase the accuracy by eliminating the region.
 Canny edge detection, HSV color thresholding and Hough transform are used to find the lane segments.
@@
 
-We can generate the lane pose for every segments according to the lane geometry.
+We can generate a single lane pose for every segments according to the lane geometry.
 The lane pose $d$ and $phi$ represent the car lateral displacement and orientation angle.
-we later feed this different poses into the histogram filter for a better prediction of the lane pose.
+we later feed the poses into the histogram filter for a better prediction of the lane pose.
 
@@
 The histogram filter works like a vote box.
-We first filter out extreme value vote by the \textbf{mode}.
-We then calculate the \textbf{mean} of the rest of the data.
+We first filter out extreme value by calculate the \textbf{mode}, then calculate the \textbf{mean} of the rest of the data.
 Higher vote pose will have higher chance to dominate the result.
@@
 
-We use the differential wheeled type car, which there are two independent motors on two side.
-The car can turn by changing the speed rate between two motors, therefore it doesn't requires a steering mechanics.
+Puyuma is a differential wheeled type car.
+There are two independent motors on two side.
+The car can be turned by changing the speed rate between two motors, therefore, it does not requires any steering mechanics.
 We use the \textbf{PID Control} algorithm to fix the orientation and lateral displacement.

### 2017-05-09 cthpc-2017/paper.tex
Describe lane following algorithm briefly

@@
 \subsection{Lane Following Algorithm}
+
+Lane following algorithm is the core of the Puyuma, it consists the lane detector algorithm and self-driving algorithm.
+Lane detector algorithm provides pose information for the unmanned vehicle.
+The pose information contains lateral displacement and orientation of car.
+
+We created an artificial environment that the lane detector can be implemented easier.
+The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection for image contour generation, HSV color thresholding method to filter out the specified color region and Hough transform for straight line detection.
+
+We first cut out the sub-region from original image to increase the accuracy and using Homography Transform to change the camera view.
+After that, we use lane detector to detects the segments and calculate lane pose due to the lane geometry.
+Histogram filter is also used to make the prediction better.
+
+After finished implementing the lane detector, we use the \textbf{PID Controller} algorithm to make the car smoothly driving on the road.
+Obstacle avoidance by using machine learning may be explored in the future.
 

### 2017-05-13 cthpc-2017/paper.tex
Reduce unnecessary description of lane following

@@
 We created an artificial environment that the lane detector can be implemented easier.
-The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection for image contour generation, HSV color thresholding method to filter out the specified color region and Hough transform for straight line detection.
+The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding      and Hough transform.
 
@@
 After finished implementing the lane detector, we use the \textbf{PID Controller} algorithm to make the car smoothly driving on the road.
-Obstacle avoidance by using machine learning may be explored in the future.
 
@@
 
-The equation of PID controller in continuous time is given as:
-
-\[e(t) = setpoint(t) - x(t)\]
-
-\[u(t) = K_p e(t) + K_i \int_{0}^{t} e(\tau) d\tau + K_d  \frac{de(t)}{dt}\]
-
-and for discrete time:
-
-\[e[t] = setpoint[t] - x[t]\]
-
-\[u[t] = K_p e[t] + K_i \sum_0^t e[t] \Delta t + K_d \frac{e[t] - e[t-1]}{\Delta t}\]
-
 The pose controller is a cascaded PID controller.
 The $\phi$ controller is a low level controller for lane orientation stabilizing, and d controller fix the lateral displacement by changing the setpoint of $\phi$ controller to turn left or right.
-The wheel control signal generating PWM is simply the throttle value plus the correction value:
-
-\begin{lstlisting}
-pwm_left = THROTTLE__BASE - pwm_correction
-pwm_right = THROTTLE__BASE + pwm_correction
-\end{lstlisting}
 
@@
 The context switching performance is important because the number of sensors can be high and we need to read data from different sensors continuously in real-time.
-Linux with real-time extension  fulfills all these criteria e.g., performance, reusability, changeability, and maintainability, whichhave significant value from the software engineer's perspective.
+Linux with real-time extension  fulfills all these criteria e.g., performance, reusability, changeability, and maintainability, which have significant value from the software engineer's perspective.
 Puyuma is released as an open source project as well as ROS, allowing further collaboration on algorithms and system integration.

### 2017-05-13 cthpc-2017/paper.tex
Improve the lane detector part

@@
 The lane segment detection is performed before pose estimation.
-The ROI(Region of interest) is used to increase the accuracy by eliminating the region.
-Canny edge detection, HSV color thresholding and Hough transform are used to find the lane segments.
+We first cut out the bottom half image, and we called this the Region of Interest (ROI).
+The reason we only left with ROI is because lane segments have much more chance to locate there due to the camera projection.
+We then use Canny edge detection for contour finding, HSV color thresholding to search for specified color region and Hough transform to detect for straight lines.
 
@@
 
-We can generate a single lane pose for every segments according to the lane geometry.
+After detecting the lines, we can generate lane pose for every segments according to the lane geometry.
 The lane pose $d$ and $phi$ represent the car lateral displacement and orientation angle.
@@
 The histogram filter works like a vote box.
-We first filter out extreme value by calculate the \textbf{mode}, then calculate the \textbf{mean} of the rest of the data.
+We first filter out extreme value by finding the \textbf{mode}, then calculate the \textbf{mean} of the rest of the data.
 Higher vote pose will have higher chance to dominate the result.

### 2017-05-14 cthpc-2017/paper.tex
Remove section "Multiple Cars Interaction"

@@
 
-\subsection{Multiple Car Interaction}
-
-\subsubsection{Apriltag}
-
-Apriltag is a visual fiducial system.
-It appears as 2D bar code and stores data like QRcode.
-The difference is that Apriltag contains less data but provides farther and clearer data fetching, regardless of the orientation of view.
-Thus, it is useful for a wide variety of tasks including augmented reality, robotics, and camera calibration.
-The AprilTag detection software computes the precise 3D position, orientation, and identity of the tags relative to the camera.
-The 36h11 Apriltag family is adopted in this project to simulate scenario, like intersections, bus stops, traffic signal and parking lot.
-
-\subsubsection{Crossroad}
-
-Instead of using traditional and inefficient traffic light, we implement central management toward city crossroads.
-Before crossing a intersection, cars send request to the server according to the apriltag nearby which determines the crossroad ID.
-We predefine several states when multiple car intend to pass through the crossroad.
-For some situation, cars can pass at the same time, and others cannot, whereas need to set a lock until one car leaves the crossroad.
-
 \section{Performance}

### 2017-05-14 cthpc-2017/paper.tex
Add lane detector work condition
Add lane following working flow
Refer article to duckietown

@@
 
-We created an artificial environment that the lane detector can be implemented easier.
+We refer to MIT Duckietown's experience \cite{Duckietown} and created an artificial environment that the lane detector can be implemented easier.
 The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding and Hough transform.
@@
 After finished implementing the lane detector, we use the \textbf{PID Controller} algorithm to make the car smoothly driving on the road.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=3in]{img/lane_flow.png}
+	\caption{lane following algorithm work flow}
+	\label{fig:lane_following_flow}
+\end{figure}
 
@@
 \end{figure}
+
+\subsubsection{Lane detector work conditions}
+$ $
+\begin{table}[!htbp]
+	\centering
+	\caption{Lane detector work conditions}
+	\label{lane_detector_condition}
+	\begin{tabular}{ll}
+		Frame rate                      &10fps \\
+		Image format                    &8-bits RGB cv::Mat \\
+		Image size                      &320x240 px	 \\	
+		ROI (Region of Interest) size   &320x120 px
+	\end{tabular}
+\end{table}
 

### 2017-05-15 cthpc-2017/paper.tex
Re-arranged the system and xenomai architecture image
Change budget form NTD to USD and correct the spelling

@@
 
+\FloatBarrier
+
 \begin{figure}
 	\centering
-	\includegraphics[width=3in]{img/arch.png}
+	\includegraphics[width=2.3in]{img/soft_arch.jpg}
 	\caption{System Architecture}
@@
 
-Despite limited the budget shown in table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car Interaction and route planning.
+Despite limited the budget shown in table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car interaction and route planning.
 
@@
 		Hardware                & Budgets  \\
-		Raspberry Pi3 Model B   & 1200 NTD \\
-		Raspberry Pi camera     & 698 NTD  \\
-		2S LiPo battery 1300mAh & 240 NTD  \\
-		Sandisk 16G microSD     & 185 NTD  \\
-		L298N motor driver      & 263 NTD  \\
-		Car frame               & 375 NTD  \\
-		DC voltage regulator    & 105 NTD  \\
-		Total                   & 3066 NTD
+		Raspberry Pi3 Model B   & 39.79 USD \\
+		Raspberry Pi camera     & 23.15 USD  \\
+		2S LiPo battery 1300mAh & 7.96 USD  \\
+		Sandisk 16G microSD     & 6.13 USD  \\
+		L298N motor driver      & 8.72 USD  \\
+		Car frame               & 12.44 USD  \\
+		DC voltage regulator    &  3.48 USD  \\
+		Total                   & 101.67 USD
 	\end{tabular}
@@
 
+\FloatBarrier
 \begin{figure}
 	\centering
-	\includegraphics[width=3in]{img/xeno_arch.png}
+	\includegraphics[width=3in]{img/xeno_arch.jpg}
 	\caption{Cobalt core in Xenomai 3}
@@
 On the contrary, using general-purpose input/output (GPIO) to simulate PWM signals is known as software PWM.
-We implement the later as a Xenomai kernel-mode real-time task to ensure the precision of PWM signal generation, named after KsoftPWM, for closed-loop control system, benefiting from the limination of system call overhead and potential locks.
+We implement the later as a Xenomai kernel-mode real-time task to ensure the precision of PWM signal generation, named after KsoftPWM, for closed-loop control system, benefiting from the elimination of system call overhead and potential locks.
 
@@
 
-Figure \ref{fig:extrinsic} show the result of Homography transformation, we exploit the transformation for the lane detectoion algorithm, the result is usually called the bird view image or inverse perspective mapping.
+Figure \ref{fig:extrinsic} show the result of Homography transformation, we exploit the transformation for the lane detection algorithm, the result is usually called the bird view image or inverse perspective mapping.
 
@@
 \bibliographystyle{IEEEtran}
-\bibliography{references}
+\bibliography{references.bib}
 

### 2017-05-15 cthpc-2017/paper.tex
Change budget form NTD to USD and correct the spelling

@@
 \usepackage{placeins}
-%\usepackage{flafter}
 
@@
 \usepackage{listings}
-% \usepackage{sectsty}
-% \usepackage{authblk}
-% \graphicspath{{../pdf/}{../jpeg/}}
-% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
 
@@
 		Hardware                & Budgets  \\
-		Raspberry Pi3 Model B   & 39.79 USD \\
+		Raspberry Pi3 Model B   & 35.00 USD \\
 		Raspberry Pi camera     & 23.15 USD  \\
@@
 		DC voltage regulator    &  3.48 USD  \\
-		Total                   & 101.67 USD
+		Total                   & 96.88 USD
 	\end{tabular}
@@
 
-We refer to MIT Duckietown's experience \cite{Duckietown} and created an artificial environment that the lane detector can be implemented easier.
+Our basic setup was inspired by MIT Duckietown \cite{Duckietown}, and we created an artificial environment where the lane detector can be implemented in straightfoward ways.
 The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding and Hough transform.
@@
 
-The intrinsic matrix is also refer to the camera projection, it is an ideal linear model consists of focal length, pixel size and principal point, the non-linear effects like lens distortion[\ref{fig:intrinsic}] are usually solved numerically.
+The intrinsic matrix is also refering to the camera projection, and it is regarded as an ideal linear model consists of focal length, pixel size and principal point, the non-linear effects like lens distortion[\ref{fig:intrinsic}] are usually solved numerically.
 
@@
 
-Figure \ref{fig:extrinsic} show the result of Homography transformation, we exploit the transformation for the lane detection algorithm, the result is usually called the bird view image or inverse perspective mapping.
+Figure \ref{fig:extrinsic} shows the result of Homography transformation, we exploit the transformation for the lane detection algorithm, the result is usually called the bird view image or inverse perspective mapping.
 
@@
 \end{figure}
-
-\subsubsection{Lane detector work conditions}
-$ $
-\begin{table}[!htbp]
-	\centering
-	\caption{Lane detector work conditions}
-	\label{lane_detector_condition}
-	\begin{tabular}{ll}
-		Frame rate                      &10fps \\
-		Image format                    &8-bits RGB cv::Mat \\
-		Image size                      &320x240 px	 \\	
-		ROI (Region of Interest) size   &320x120 px
-	\end{tabular}
-\end{table}
 
@@
 We also compare performance among KsoftPWM, non-real-time PWM kernel module (nRTPKM) and WiringPi \cite{WiringPi}, the most famous library for GPIO controlling on Raspberry Pi 3 (Broadcom bcm2709 SoC, 1.2GHz ARM Cortex-A53 CPU).
-The background system load was generated by Linux Test Project (LTP), which provides a collection of tools for validating the reliability, robustness, and stability of Linux.
+The background system load was generated by Linux Test Project (LTP) \cite{LTP}, which provides a collection of tools for validating the reliability, robustness, and stability of Linux.
 Unit of latency is microsecond in all measurement.
@@
 Real-time performance is measured by stressing the system with LTP and applying cyclictest.
-We use LTP $-i$ and $-c$ flags to specify the background CPU load with multiple processes and accessing on IO bus.
+\cite{cyclictest} We use LTP $-i$ and $-c$ flags to specify the background CPU load with multiple processes and accessing on IO bus.
 Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in Figure \ref{fig:xeno_perf_modify}.
 Table \ref{xeno_compare} records the maximum latency for Xenomai.
+
+\subsection{Lane detector Performance}
+
+The current state lane detector is implemented under OpenCV 2.4 and using single CPU core without GPU acceleration, further hardware optimization like: NEON, Intel TBB may help to speed up the overall performance.
+
+\begin{table}[!htbp]
+	\centering
+	\caption{Lane detector performance and test conditions}
+	\label{lane_detector_condition}
+	\begin{tabular}{ll}
+		Frame rate                      &10fps \\
+		Image format                    &8-bits RGB cv::Mat \\
+		Image size                      &320x240 px	 \\	
+		ROI (Region of Interest) size   &320x120 px
+	\end{tabular}
+\end{table}
 

### 2017-05-15 cthpc-2017/paper.tex
Add the reference for LTP and cyclictest

--- 2017-05-15 cthpc-2017/paper.tex
@@
 Real-time performance is measured by stressing the system with LTP and applying cyclictest.
-We use LTP $-i$ and $-c$ flags to specify the background CPU load with multiple processes and accessing on IO bus.
+\cite{cyclictest} We use LTP $-i$ and $-c$ flags to specify the background CPU load with multiple processes and accessing on IO bus.
 Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in Figure \ref{fig:xeno_perf_modify}.

### 2017-05-15 cthpc-2017/paper.tex
Fix grammar errors
Move the lane detector performace to the right place
Wording tweaks

--- 2017-05-15 cthpc-2017/paper.tex
@@
 
-The system is designed for multiple self-driving cars, enabling collaborative computer vision, map navigation, motor control, and wireless communications, shown in Figure \ref{fig:overall_arch}.
-It aggregates local pose graphs obtained from its multiple cars into a global pose graph, which it then feeds back to the cars to increase their mapping and localization effectiveness.
+Various hardware components e.g., sensors, motors, wireless devices, and ARM SoC are used for a self-driving miniature vehicle. When selecting the cost-efficient components, the general
+selection criteria were efficiency, low-power consumption, low-price, availability and extendability.
+
+The system allows the existence of multiple self-driving cars, enabling collaborative computer vision, map navigation, motor control, and wireless communications, shown in Figure \ref{fig:overall_arch}.
+It aggregates local pose graphs obtained from its multiple cars into a global pose graph, which it then reacts to the cars to increase their mapping and localization effectiveness.
 
@@
 
-Despite limited the budget shown in table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car interaction and route planning.
+Despite limited the budget shown in Table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car interaction and route planning.
 
@@
 
-Our basic setup was inspired by MIT Duckietown \cite{Duckietown}, and we created an artificial environment where the lane detector can be implemented in straightfoward ways.
+Our basic configuration was inspired by MIT Duckietown \cite{Duckietown}, and we created an artificial environment where the lane detector can be implemented in straightfoward ways.
 The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding and Hough transform.
@@
 
-The camera was calibrated before activating the controller. Two parameters are used to describe the relationship between image and real world: intrinsic matrix and extrinsic matrix.
+The camera was calibrated before we activated the controller. Two parameters are used to describe the relationship between image and real world: intrinsic matrix and extrinsic matrix.
 
@@
 The extrinsic matrix represents the rotation and translation of camera with respect to the world.
-A linear transformation called Homograpy is applied on  the matrix to change the camera view purely mathematically.
+A linear transformation called Homograpy is applied to the matrix, changing the camera view purely mathematically.
 
@@
 		Image size                      &320x240 px	 \\	
-		ROI (Region of Interest) size   &320x120 px
+		ROI size                        &320x120 px
 	\end{tabular}

### 2017-05-15 cthpc-2017/paper.tex
Mention further improvements about OpenCV

@@
 \begin{tabular}{llll}
-                              & User task & Kernel task & Irq task \\
+                              & User task & Kernel task & IRQ task \\
 Xenomai with original kernel  & 76.067 us & 36.262 us   & 27.895us \\
@@
 
-The current state lane detector is implemented under OpenCV 2.4 and using single CPU core without GPU acceleration, further hardware optimization like: NEON, Intel TBB may help to speed up the overall performance.
+At present, the algorithms of lane detector is implemented by using with OpenCV version 2.4 as single-threaded task without specified CPU or GPU accelerations but yet leads to reasonaly fast response time while collaboring to ROS framework as Table \ref{lane_detector_condition} indicates.
 
@@
 \end{table}
+
+It is possible to build 30\% faster OpenCV packages \cite{faster-opencv} optimized for Raspberry Pi 3 via ARM's advanced SIMD instruction \cite{arm-neon} and Intel's Threading Building Blocks \cite{intel-tbb} where the whole lane detector can be accelerated with code modifications.
 
